### 2019-08-29 Manuscript/Manuscript.tex

We thank Alec Brenner, Sam Lo Bianco, Mariana Lin, and Judy Pu for their contributions to the paleoshoreline reconstructions. Collaborative research between NLS-H and YG was initially supported by the France-Berkeley Fund. FAM and NLS-H thank NSF FRES grant #20191023 for support.

\section*{TABLES}

XXX

@@

\begin{figure}
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/shoreline_growth.pdf}
    \caption{The emergence of Indonesia and New Guinea. Past shorelines are shown in A with resultant area estimates summarized in B. A significant increase in area over the past 5 million years is coincident with cooling and the onset of Northern Hemisphere glaciation as reflected in the benthic oxygen isotope record in C \cite{Zachos2008a}.}
    \label{fig:shoreline_growth}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/scenario_pCO2.pdf}
    \caption{Box shows quartiles, whiskers show 1.5$\times$ the interquartile range, notch shows median with 95\% confidence interval. Each dot shows a parameter combination. Dashed line is PI \pCOtwo.}
    \label{fig:scenario_pCO2}
\end{figure}

>>>>

We thank Alec Brenner, Sam Lo Bianco, Mariana Lin, and Judy Pu for their contributions to the paleoshoreline reconstructions. Collaborative research between NLS-H and YG was initially supported by the France-Berkeley Fund. FAM and NLS-H thank NSF FRES grant \#20191023 for support.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{Manuscript/Figures/shoreline_growth.pdf}
    \caption{The emergence of Indonesia and New Guinea. Past shorelines are shown in A with resultant area estimates summarized in B. A significant increase in area over the past 4 million years is coincident with cooling and the onset of Northern Hemisphere glaciation as reflected in the benthic oxygen isotope record in C \citep{Zachos2008a}.}
    \label{fig:shoreline_growth}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/scenario_pCO2.pdf}
    \caption{Box shows quartiles, whiskers show 1.5$\times$ the interquartile range, notch shows median with 95\% confidence interval. Each dot shows a parameter combination. Dashed line is PI \pCOtwo.}
    \label{fig:scenario_pCO2}
\end{figure}
